Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-01-08 paper.tex
docs: resuts
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

The magnitude of U Cephei varies from 6.7 to 9.2. Which is actually a huge variation in brightness. If we wanna have a comparaison in percentage we can do the following calculation:

@@

Using \href{https://siril.org/fr/}{Siril} which is a free and opensource software for astrophotography, it is very easy to align all the images of the observation to make sure the star is always at the same place in the frame.
As a comparaison here is the same data after the cleaning process:

@@

@@

The light curve of U Cephei is showing a clear transit event happening, we can see the flux of the star decreasing and then increasing again, as comparaison to the flux of the comparison star.
I didn't completely trim the data after the transit to showcase the return to normal of the star, we see that from 0.62 to the end the curve seems to stabilize again and become linear.

@@

This is a great result, it means that the observation was successful and that we managed to catch a transit event, now it is time to compare it to data that was collected by professional observatories.

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{assets/comparaison.png}
    \caption{Light curve comparaison from TESS data and amateur data.}
    \label{fig:tess-data-comparaison}
\end{figure}

One thing we see when looking at those light curves is the fact they are not overlapping. This can be explained by the fact that TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter. It could also be explained by the fact
TESS sensor is more sensitive than the one used in this study, making the star looks brighter. This is why the data is not overlapping, but the transit event is still clearly visible on both light curves.

\begin{itemize}
    \item Amateur data demonstrated significant precision in detecting transit features, with signal-to-noise ratios that were competitive with professional datasets under optimal conditions.
    \item Light pollution and equipment limitations introduced variability, leading to slightly higher error margins compared to professional datasets.
    \item Cross-validation with professional data confirmed the overall reliability of the amateur observations, with minor deviations attributed to observational conditions.
\end{itemize}
Figures and tables summarizing the comparative results are presented below.

>>>>

The magnitude of U Cephei varies from 6.7 to 9.2. Which is actually a huge variation in brightness. If we wanna have a comparison in percentage we can do the following calculation:

@@

Using \href{https://siril.org/fr/}{Siril} which is a free and opensource software for astrophotography, it is very easy to align all the images of the observation to make sure the star is always at the same place in the frame.
As a comparison here is the same data after the cleaning process:

@@

In this graph, we see multiple lines: the blue one represents the normalized relative flux of U Cephei, while the red and green ones show the normalized relative flux of the comparison stars. The flux of the comparison stars remains fairly linear around 1, 
whereas the flux of U Cephei follows a parabolic curve, starting from 1.5, decreasing to 0.6, and then returning to 1.5 over 9.6 hours. This duration is calculated as \( 0.7 - 0.3 = 0.4 \, \text{days} \), and \( 0.4 \, \text{days} \times 24 = 9.6 \, \text{hours} \).

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{assets/comparison.png}
    \caption{Light curve comparison from TESS data and amateur data.}
    \label{fig:tess-data-comparison}
\end{figure}

This graphs shows the light curve of U Cephei from the TESS data in blue and the amateur data I collected in orange. 
Both curves display a parabolic similar shape. The TESS data light curve actually being a bit brighter, starting around 6.85 and lowering to almost 8.25 than the amateur one, starting at 7.75 and lowering to 8.75.

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{assets/shifted-comparison.png}
    \caption{Light curve comparison where the amateur data was shifted by -0.5.}
  \label{fig:tess-data-comparison-shifted}
\end{figure}

This is another light curve comparison very similar to the previous one, but this time the amateur data has been shifted by -0.5.

\subsection{Figure 1}

@@

The light curve of U Cephei is showing a clear transit event happening.

This is a great result, it means that the observation was successful and that we managed to catch a transit event, now it is time to compare it to data that was collected by professional observatories.
\medskip

@@

\subsection{Figure 2}
One thing we see when looking at those light curves is the fact they are not overlapping. This can be explained by the fact that TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter. It could also be explained by the fact
TESS sensor is more sensitive than the one used in this study, making the star looks brighter. This is why the data is not overlapping, but the transit event is still clearly visible on both light curves.

\subsection{Figure 3}
